### 2024-01-04 tesis_Ashish/Chapter5/chapter5.tex
Updated thesis 4 Jan 2024

To investigate the performance of the PCC luminometer during the 2022 data collection period, we segment CMS luminosity data into five distinct periods:  C, D, E, F, and G, as illustrated in Figure \ref{fig:period_bound_1}. The run ranges associated with each of these periods are outlined in Fig. \ref{fig:period_bound_1}. Notably, during period F, specifically during Fill 8381, van der Meer (vdM) scans were implemented to calibrate the PCC luminometer. For our current analysis, we employ dataset that align with the 2022 luminosity measurement periods, specifically 2022C, 2022D, 2022E, and 2022F, Run 2022G as highlighted in Table \ref{tab:my_label_1}. We extracted these datasets from the Alignment and Calibration (AlCa) project, a critical aspect of the CMS experiment. The selected datasets encompass two subcategories, namely Random trigger and Zero Bias similar to Run 2 PCC dataset. %The Random trigger dataset includes data where triggers are applied to both colliding and non-colliding bunches and the Zero Bias dataset consists of events that have successfully navigated the trigger system without any bias (no use of CMS detector signal), in this case, the trigger is applied exclusively to the colliding bunches.

>>>>

To investigate the performance of the PCC luminometer during the 2022 data collection period \cite{Hayrapetyan:2870088}, we segment CMS luminosity data into five distinct periods:  C, D, E, F, and G, as illustrated in Figure \ref{fig:period_bound_1}. The run ranges associated with each of these periods are outlined in Fig. \ref{fig:period_bound_1}. Notably, during period F, specifically during Fill 8381, van der Meer (vdM) scans were implemented to calibrate the PCC luminometer. For our current analysis, we employ dataset that align with the 2022 luminosity measurement periods, specifically 2022C, 2022D, 2022E, and 2022F, Run 2022G as highlighted in Table \ref{tab:my_label_1}. We extracted these datasets from the Alignment and Calibration (AlCa) project, a critical aspect of the CMS experiment. The selected datasets encompass two subcategories, namely Random trigger and Zero Bias similar to Run 2 PCC dataset. %The Random trigger dataset includes data where triggers are applied to both colliding and non-colliding bunches and the Zero Bias dataset consists of events that have successfully navigated the trigger system without any bias (no use of CMS detector signal), in this case, the trigger is applied exclusively to the colliding bunches.

### 2024-01-04 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 4 Jan 2024

We study the linearity of two-fold coincidences that is how the number of two-fold coincidences change with pileup to obtain precise luminosity measurement. Distribution of two-fold coincidences for TEPX Disk 4 Ring 1 for all pileup values is shown in Fig. \ref{fig:tepx_coin_allPU}. For pileup 200, mean two-fold coincidences is around 270. The new algorithm is able to suppress non-linearity at high pileup values as shown in Fig.  \ref{fig:CMS_420}  and \ref{fig:CMS_4207}. Non-linearity is within 1 \% for entire pileup range.

>>>>

We study the linearity of two-fold coincidences that is how the number of two-fold coincidences change with pileup to obtain precise luminosity measurement \cite{sehrawat2022optimisation}. Distribution of two-fold coincidences for TEPX Disk 4 Ring 1 for all pileup values is shown in Fig. \ref{fig:tepx_coin_allPU}. For pileup 200, mean two-fold coincidences is around 270. The new algorithm is able to suppress non-linearity at high pileup values as shown in Fig.  \ref{fig:CMS_420}  and \ref{fig:CMS_4207}. Non-linearity is within 1 \% for entire pileup range.
